Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-05 WSSSPE3/report/wg_main_metrics.tex
small change to change in 5.6

Metrics for scientific software are important for tenure and promotion,
scientific impact, discovery, reducing duplication, serving as a basis for
potential industrial interest in adopting software, prioritizing development and
support towards strategic objectives, and making a case for new or continued
funding. However, there is no commonly-used standard for collecting or
presenting metrics, nor is it known if there is a common set of metrics for
scientific software. It is imperative that scientific software stakeholders
understand that it is useful to collect metrics.

>>>>

Metrics for scientific software are important for many purposes, including tenure and promotion,
scientific impact, discovery, reducing duplication, serving as a basis for
potential industrial interest in adopting software, prioritizing development and
support towards strategic objectives, and making a case for new or continued
funding. However, there is no commonly-used standard for collecting or
presenting metrics, nor is it known if there is a common set of metrics for
scientific software. It is imperative that scientific software stakeholders
understand that it is useful to collect metrics.
